Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-01 neurips-20/cvx-flats.tex
pass through Section 3 - looks good!

\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}
%While the subtleties of \emph{consistency} vary slightly within the literature, we use two definitions that have the same implications, but one may be more appropriate than the other in a given context.

In this section, we show that indirect elicitation gives a single necessary condition for consistency that applies to all of the above settings (our four quadrants).
In discrete predictions, it is well-known that a surrogate is consistent with respect to a target loss if and only if it is calibrated with respect to the target (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
We can show Theorem~\ref{thm:consistent-implies-indir-elic} through calibration (and even extend the definition of calibration to have meaning in continuous estimation), but calibration requires being given a target loss, which is not always guaranteed.
We delegate this proof to Appendix~\ref{app:calibration} when one is given a target loss and directly prove the general result, which does not rely on a target loss.
%This criterion is implied by both consistency and calibration, as fully explored in Appendix~\ref{app:calibration},
\raft{I really like the flow here, but was thinking of a slightly longer version of the nod to calibration.  Like ``You may be wondering if we could leverage ``consistency $\iff$ calibration'' to prove this.  We can, and can even extend that definition to a meaningful version for continuous predictions, but even this general calibration definition relies on a target loss being given.  We therefore delegate those details to Appendix X and directly prove the general result, which also handles the case when a loss is not given.''} \jessiet{Attempted to add some of this discussion}
Since this criterion is implied by both consistency and calibration, it might be viewed as a weak necessary condition for existence of a consistent dimension-$d$ surrogate, yet it gives state-of-the-art lower bounds on $d$.
In particular, indirect elicitation bounds imply feasible subspace dimension bounds.

We start by formalizing consistency in two ways that generalize across our four quadrants.
First, given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition \ref{def:consistent-ell}).
Second, given a property $\gamma$ (for example, the $\alpha$-quantile)\jessiet{changed example from conditional mean}, then we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions (Definition \ref{def:consistent-prop}).
We will then show that consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.

@@

If $\gamma$ is an elicitable property, and is elicited by $\ell$, then the two definitions are equivalent when using target regret as $\propdis$.
\begin{lemma}\label{lem:consistent-loss-implies-prop}
	Suppose we are given a surrogate loss $L$ and link $\psi$, and target loss $\ell$.
	Consider $\propdis: \R \times \simplex \to \reals_+$ with $\mu(r,p) := R_\ell(r,p)$.
	$(L, \psi)$ are consistent with respect to $\ell$ if and only if they are $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	First, observe that $\propdis(r,p) = 0 \iff r \in \gamma(p)$, since $r \in \gamma(p)$ implies $\ell(r;p) = \risk{\ell}(p)$, and if $r \not \in \gamma(p)$, then $\ell(r;p) > \risk{\ell}(p)$.

@@

Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\citte{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.
Thus, the result also applies to extend previous results~\citep{frongillo2015elicitation,frongillo2018elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.

>>>>

\section{Consistency implies indirect elicitation}\label{sec:consis-implies-indir}

\botodo{Made small changes to emphasize that prior calibration results focus on one quadrant.}
In this section, we show in Theorem \ref{thm:consistent-implies-indir-elic} that indirect elicitation is necessary for consistency.
This gives a single necessary condition for consistency that applies to all of the above settings (our four quadrants).
For the quadrant of discrete predictions with a target loss function, it is well-known that a surrogate is consistent if and only if it is calibrated (e.g.\,~\citep[Theorem 1, part 3]{bartlett2006convexity}).
For this case, we can show Theorem~\ref{thm:consistent-implies-indir-elic} via calibration, and even extend the definition of calibration and proof approach to the quadrant with a target loss and continuous prediction space.
We delegate this proof to Appendix~\ref{app:calibration} and directly prove the general result, which applies to target properties as well as target losses.
%This criterion is implied by both consistency and calibration, as fully explored in Appendix~\ref{app:calibration},
\raft{I really like the flow here, but was thinking of a slightly longer version of the nod to calibration.  Like ``You may be wondering if we could leverage ``consistency $\iff$ calibration'' to prove this.  We can, and can even extend that definition to a meaningful version for continuous predictions, but even this general calibration definition relies on a target loss being given.  We therefore delegate those details to Appendix X and directly prove the general result, which also handles the case when a loss is not given.''} \jessiet{Attempted to add some of this discussion} \botodo{A bit of rephrasing to try to be clearer.}
Since indirect elicitation is implied by both consistency and calibration, it might seem a very weak necessary condition for existence of a consistent dimension-$d$ surrogate.
Yet, it gives state-of-the-art lower bounds on $d$.
In particular, we will derive bounds that imply those given by the feasible subspace dimension approach.

We start by formalizing consistency in two ways that generalize across our four quadrants.
First, given an original loss $\ell$, then we say $L$ is consistent if optimizing $L$ implies optimizing $\ell$ (Definition \ref{def:consistent-ell}).
Second, given a property $\gamma$ (for example, the $\alpha$-quantile), we say $L$ is consistent if optimizing $L$ implies approaching, in some sense, the correct statistic $\gamma(D_x)$ of the conditional distributions (Definition \ref{def:consistent-prop}).
We will then show that consistency always implies $L$ indirectly elicits $\prop{\ell}$ or $\gamma$ respectively.

@@

If $\gamma$ is an elicitable property, and is elicited by $\ell$, then the two definitions are equivalent when using target regret of $r$ (compared to an optimal prediction for $p$) as $\propdis(r,p)$.
\begin{lemma}\label{lem:consistent-loss-implies-prop}
	Suppose we are given a surrogate loss $L$ and link $\psi$, and target loss $\ell$.
	Consider $\propdis: \R \times \simplex \to \reals_+$ with $\mu(r,p) := R_\ell(r,p)$.
	$(L, \psi)$ are consistent with respect to $\ell$ if and only if they are $\propdis$-consistent with respect to $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	First, observe that $\propdis(r,p) = 0 \iff r \in \gamma(p)$, since $r \in \gamma(p)$ implies $\ell(r;p) = \risk{\ell}(p)$, and if $r \not \in \gamma(p)$, then $\ell(r;p) > \risk{\ell}(p)$.

@@

Theorem~\ref{thm:cvx-flats} also addresses one major open question from~\cite{frongillo2015elicitation,frongillo2018elicitation}\jessiet{which citation?}: \emph{what are lower bounds on convex elicitation complexity?}
While Theorem~\ref{thm:cvx-flats} is a statement about consistent surrogates, the heart of it is actually about indirect property elicitation.
Thus, the result also applies to extend previous results~\citep{frongillo2015elicitation,frongillo2018elicitation} to provide new bounds on elicitation complexity for certain classes of properties in Theorem~\ref{thm:bayes-risk-lower-bound}.
